Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-11-28 paper1.tex
final changes for co-authors

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. Boada et al.]
{\parbox{\textwidth}{Steven~Boada,$^{1,2}$\thanks{E-mail: boada@physics.rutgers.edu}
C.~Papovich,$^{2}$
R.~Wechsler,$^{3,4}$
T.~S.~Li,$^{7}$
K.~Gebhardt,$^{6}$
J.~DeRose,$^{3}$
E.~Rozo,$^{3,5}$
E. S.~Rykoff$^{3}$}\vspace{0.4cm}\
\\
\parbox{\textwidth}{$^{1}$Physics and Astronomy Department, Rutgers University, Piscataway, NJ 08854-8019, USA\\
$^{2}$George P.\ and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242, USA\\
$^{3}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{4}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{5}$Department of Physics, University of Arizona, Tucson, AZ 85721, USA\\
$^{6}$Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA\\
$^{7}$Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. Boada et al.]
{\parbox{\textwidth}{Steven~Boada,$^{1,2}$\thanks{E-mail: boada@physics.rutgers.edu}
C.~Papovich,$^{2}$
R.~Wechsler,$^{3,4}$
J.~DeRose,$^{3}$
T.~S.~Li,$^{7}$
K.~Gebhardt,$^{6}$
G.~Hill,$^{6}$
E.~Rozo,$^{3,5}$
E. S.~Rykoff~$^{3}$}\vspace{0.4cm}\
\\
\parbox{\textwidth}{$^{1}$Physics and Astronomy Department, Rutgers University, Piscataway, NJ 08854-8019, USA\\
$^{2}$George P.\ and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242, USA\\
$^{3}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{4}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{5}$Department of Physics, University of Arizona, Tucson, AZ 85721, USA\\
$^{6}$Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA\\
$^{7}$Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}}
